The Evolution of Phenotypically Invariant Genetic Networks

### 2017-12-06 kalman_walk_paper.tex
reparameterized and some formatting edits

  \begin{figure}[H]
  \label{fig:osc_incompat}
    \centering
    %\begin{tabular}{cc}
    %\includegraphics[width=0.4\textwidth]{figures/f1_quartic2} &
    %\includegraphics[width=0.4\textwidth]{figures/f2_quad2}
    %\end{tabular}
    \includegraphics[width=0.5\textwidth]{examples/F2_vs_F1_divergence_tau0}
   % \caption{
    %\textbf{(left)} 
    \caption{Phenotype distance to optimum, $D$, using $\rho(t) = \exp(-t/4\pi)$
    for $F_1$ (red) and $F_2$ (blue) hybrids between an $A(0)$ and an $A(\epsilon)$ parent. Genetic distance is computed as the Frobenius norm between two systems.}
    %\textbf{(right)} Same, but for $F_2$ offspring (one line per type of $F_2$).
    %\plri{make this $D$ not $D^2$ and say which line is the overall average $F_2$.
    %}
    \label{fig:osc_incompat}
  \end{figure}
\end{example}

>>>>

  \begin{figure}[H]
  \label{fig:osc_incompat}
    \centering
    %\begin{tabular}{cc}
    %\includegraphics[width=0.4\textwidth]{figures/f1_quartic2} &
    %\includegraphics[width=0.4\textwidth]{figures/f2_quad2}
    %\end{tabular}
    \includegraphics[width=0.5\textwidth]{examples/F2_vs_F1_divergence_tau0}
   % \caption{
    %\textbf{(left)} 
    \caption{Phenotype distance to optimum, $D$, using $\rho(t) = \exp(-t/4\pi)$
    for $F_1$ (black) and $F_2$ (blue) hybrids between an $A(0)$ and an $A(\epsilon)$ parent. Genetic distance is computed as the Frobenius norm between two systems.}
    %\textbf{(right)} Same, but for $F_2$ offspring (one line per type of $F_2$).
    %\plri{make this $D$ not $D^2$ and say which line is the overall average $F_2$.
    %}
    \label{fig:osc_incompat}
  \end{figure}
\end{example}
